The impacts of park access on health outcomes: A spatial comprehensive approach

### 2019-02-22 manuscript.Rnw
Improve data summary table

\usepackage{url}

@@

bind_rows(tract_summary, park_summary) %>%
  separate(variable, c("var", "desc"), sep = ": ") %>%
  kable(escape = FALSE, digits = 2,
        table.envir = "table*", booktabs = TRUE,
        caption = "Descriptive Statistics of Tract and Park Variables",
        col.names = c(" ", "Description", "Minimum", "Median (IQR)", "Maximum", "Source")) %>%
  kable_styling() %>%
  group_rows(paste("Tract Variables, N =", nrow(tracts)), 1, 14) %>%
  group_rows(paste("Park Variables, N =", nrow(parks)), 15, 16)

@@

tracts.dnn <- dnearneigh(gCentroid(as(pop_weighted_centroids, "Spatial"), byid = TRUE),
                         0, 1.8 * 5280)
dists <- nbdists(tracts.dnn, gCentroid(tracts, byid = TRUE))
dists.inv <- lapply(dists, function(x) 1 / x)
W <- nb2listw(neighbours = tracts.dnn, glist = dists.inv,
              zero.policy = TRUE, style = "W")
trMC <- trW(as(W, "CsparseMatrix"), type="MC") # trace used in montecarlo impacts
@
This is a similar specification to that used by  \citet{tra_autoregression_paper} 
in a study of home prices in Atlanta. We selected this specification after 
comparing overall model likelihoods between it and an adjacent (queen)
tract specification.

@@

<<distances, warning=FALSE>>=
# calculate centroids of tracts and parks
parks <- parks %>% st_transform(st_crs(pop_weighted_centroids))

# distances from all tracts to all zones
distances <- st_distance(pop_weighted_centroids, parks, byid = TRUE) %>%
  units::set_units(miles) %>%
  units::drop_units()

>>>>

\usepackage{url}
\usepackage{array}
\usepackage{pdflscape}
\usepackage{makecell}

@@

bind_rows(tract_summary, park_summary) %>%
  separate(variable, c("var", "desc"), sep = ": ") %>%
  mutate(
    msd = str_replace(msd, " \\(", "\\\\\\\\ \\("),
    msd = str_c("\\makecell{", msd, "}")
  ) %>%
  kable(escape = FALSE, digits = 2,
        table.envir = "table*", booktabs = TRUE, 
        caption = "Descriptive Statistics of Tract and Park Variables",
        col.names = c(" ", "Description", "Minimum", "Median (IQR)", "Maximum", "Source")) %>%
  kable_styling(latex_options = "scale_down") %>%
  column_spec(1, width = "0.5in") %>%
  column_spec(2, width = "2in") %>%
  group_rows(paste("Tract Variables, N =", nrow(tracts)), 1, 14) %>%
  group_rows(paste("Park Variables, N =", nrow(parks)), 15, 16)

@@

# determine which tracts are neighbors of each other. Need to be less than
# 1.8 miles away from the centroids
tracts.dnn <- dnearneigh(as(pop_weighted_centroids, "Spatial"), 0, 1.8 * 5280)
# calculate the inverse distance to use as a weight on the neighbor connection
dists <- nbdists(tracts.dnn, as(pop_weighted_centroids, "Spatial"))
dists.inv <- lapply(dists, function(x) 1 / x)
# get the spatial weights matrix and its trace to use in any impact analyses
W <- nb2listw(neighbours = tracts.dnn, glist = dists.inv,
              zero.policy = TRUE, style = "W")
trMC <- trW(as(W, "CsparseMatrix"), type="MC") # trace used in montecarlo impacts
@
This is a similar specification to that used by  \citet{tra_autoregression_paper}
in a study of home prices in Atlanta. We selected this specification after
comparing overall model likelihoods between it and an adjacent (queen)
tract specification.

@@

<<distances, warning=FALSE>>=
# project the parks data into the same projection system as the tracts
parks <- parks %>% st_transform(st_crs(pop_weighted_centroids))

# distances from all tract centroids to all parks
distances <- st_distance(pop_weighted_centroids, parks, byid = TRUE) %>%
  units::set_units(miles) %>%
  units::drop_units()
